\chapter{Disney References} \label{app:references}

\begin{list}{-}{}
    \item \textbf{Diffuse and Retro-Reflection}
    \begin{list}{-}{}
        \item original explanation, section 5.3 \cite{burley_physically_2012}
        \item refactor, eq. 4 \cite{burley_extending_2015}
    \end{list}
    \item \textbf{Specular BRDF}
    \begin{list}{-}{}
        \item Fresnel term, section 5.4 \cite{burley_physically_2012}
        \item Masking-Shadowing term, eq. 98 \cite{heitz_understanding_2014}
        \item Normal Distribution Function (NDF), eq. 85 \cite{heitz_understanding_2014}
        \item original NDF, eq. 13 \cite{burley_physically_2012}
        \item Visible NDF (VNDF) \cite{heitz_sampling_2018}
    \end{list}
    \item \textbf{Specular BTDF}
    \begin{list}{-}{}
        \item Transmission Cases, section 4 \cite{walter_microfacet_2007} 
        \item NDF, eq. 35, eq. 36 \cite{walter_microfacet_2007}
        \item Half-Vector, eq. 16 \cite{walter_microfacet_2007}
        \item Fresnel term, eq. 8 \cite{burley_extending_2015}
    \end{list}
    \item \textbf{Clearcoat}
    \begin{list}{-}{}
        \item Fresnel term, section 5.4 \cite{burley_physically_2012}
        \item Masking-Shadowing term, eq. 98 \cite{heitz_understanding_2014}
        \item Masking-Shadowing details, section 5.6 \cite{burley_physically_2012}
        \item Normal Distribution Function (NDF), eq. 4 \cite{burley_physically_2012}
    \end{list}
    \item \textbf{Sheen}
    \begin{list}{-}{}
        \item Sheen details, Addenda \cite{burley_physically_2012}
    \end{list}
    \item \textbf{Implementations}
    \begin{list}{-}{}
        \item Blender \cite{blender_foundation_blender_2022}
        \item BRDF Explorer \cite{disney_studios_brdf_2022}
        \item SORT Renderer \cite{jiayincao_sort_2022}
        \item PBRTv3 Implementation \cite{matt_pharr_pbrt_2022}
        \item Nvisii \cite{nathan_morrical_and_jonathan_tremblay_and_yunzhi_lin_and_stephen_tyree_and_stan_birchfield_and_valerio_pascucci_and_ingo_wald_nvisii_2022}
    \end{list}
\end{list}
